QPLIB: A Library of Quadratic Programming Instances

### 2017-01-27 QPLIB.tex
make references clickable in pdf
- include hyperref package
move solvers section before algorithms section
- as in the algorithms section, we refer which solver implements what
rename QPLIB-2.3 and QPLIB-2.4
- QPLIB-2.4 now contains Section 2.3
- QPLIB-2.3 now contains Section 2.4
add latex defines for solver names
- to make it easier to change their writing throughout the paper
change capitalization of solver names
- use the variant found in solver logs
- drop the FICO for xpress again (they insisted on it when we did the
  minlp software paper, but their own log is not filled up with FICO)
-

\usepackage{url}
\usepackage{secdot}
\usepackage{color}
\usepackage{booktabs}
\usepackage{amsmath,amsfonts,amssymb}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{multirow}
\usepackage{todonotes}

\usepackage{longtable}
\usepackage{enumitem}
\usepackage{calc}

@@

@@

\newenvironment{proof}[1][Proof]{\textbf{#1.} }{\ \rule{0.5em}{0.5em}}
%\renewenvironment{proof}{{\bfseries Proof}}{\qed}

\def\remark{\stepcounter{theorem}\par{\bf Remark}.
\ignorespaces}
\def\endremark{ \vbox{\hrule\hbox{%
    \vrule height1.3ex\hskip0.8ex\vrule}\hrule
   }\par}

\newenvironment{keywords}{\vspace{0.4in}\begin{quote}\small \em
{\bf Keywords\/}:}{\end{quote}}
\fi

@@

@@

\institute{Fabio Furini \at
           LAMSADE, Universit{\'e} Paris Dauphine, 75775 Paris, France.
           \email{fabio.furini@dauphine.fr}
%
\and
           Emiliano Traversi \at
           LIPN, Universit{\'e} de Paris 13, 93430 Villetaneuse, France.
           \email{emiliano.traversi@lipn.fr}
%
\and       Pietro Belotti \at
           Xpress-Optimizer team, FICO, Birmingham UK
           \email{pietrobelotti@fico.com}
%
\and       Antonio Frangioni \at
           Dipartimento di Informatica, Universit\`a di Pisa,
           Largo B. Pontecorvo 2, 56127 Pisa, Italy,
           \email{frangio@di.unipi.it}
%
\and       Ambros Gleixner \at
           Zuse Institute Berlin, Takustr. 7, 14195 Berlin, Germany.
           \email{gleixner@zib.de}
%
\and       Nick Gould \at
           STFC-Rutherford Appleton Laboratory, Chilton, Oxfordshire OX11 0QX,
           England.
           \email{nick.gould@stfc.ac.uk}
%
\and       Leo Liberti \at
           CNRS LIX, Ecole Polytechnique, 91128 Palaiseau, France.
           \email{liberti@lix.polytechnique.fr}
%
\and       Andrea Lodi \at
           Ecole Polytechnique de Montréal, Canada.               \email{andrea.lodi@polymtl.ca}
%
\and       Ruth Misener \at
           Department of Computing,Imperial College London, UK. \email{r.misener@imperial.ac.uk}
%
\and       Hans Mittelmann \at
           School of Mathematical and Statistical Sciences, Arizona State University,      Tempe, AZ 85287-1804, U.S.A.
\email{mittelmann@asu.edu}
%
\and       Nick Sahinidis \at
Chemical Engineering, Carnegie Mellon University, U.S.A. \email{sahinidis@cmu.edu}
%
\and       Stefan Vigerske \at
           GAMS Software GmbH, c/o Zuse Institute Berlin, Takustr. 7, 14195 Berlin, Germany.
           \email{svigerske@gams.com}
%
\and       Angelika Wiegele \at
Institut f{\"u}r Mathematik, Alpen-Adria-Universit{\"a}t Klagenfurt, 9020 Klagenfurt am W{\"o}rthersee, Austria.  \email{angelika.wiegele@aau.at}
           }

@@

\begin{abstract}
 This paper describes a new instance library for Quadratic Programming (QP).
 QP is a very ``varied'' class, comprising sub-classes of problems ranging from
 trivial to undecidable. Solution methods for QP are very diverse, ranging from
 entirely combinatorial ones to completely continuous ones, including many for
 which both aspects are fundamental. Selecting a set of instances of QP that is
 at the same time not overwhelmingly numerous and sufficiently challenging for the
 many different interested communities is therefore important. We propose a simple
 taxonomy for QP instances that leads to a systematic problem selection mechanism.
 We then briefly survey the field of QP, giving an overview of theory, methods and
 solvers. Finally we describe how the library was put together, and detail its final
 contents.
\end{abstract}

@@

\input{QPLIB-2.3.tex}

@@

\input{QPLIB-2.4.tex}

@@

\input{QPLIB-4.tex}

@@

>>>>

\usepackage{url}
\usepackage{secdot}
\usepackage{color}
\usepackage{booktabs}
\usepackage{amsmath,amsfonts,amssymb}
\usepackage{multirow}
\usepackage{longtable}
\usepackage{enumitem}
\usepackage{calc}
\usepackage[hidelinks]{hyperref}
\usepackage{xspace}
\usepackage[numbers,sort&compress]{natbib}
\usepackage{doi}

% TODO remove these before submission
\usepackage{todonotes}
%\usepackage{showlabels}

@@

\def\alphaecp{\textsc{AlphaECP}\xspace}
\def\antigone{\textsc{ANTIGONE}\xspace}
\def\baron{\textsc{BARON}\xspace}
\def\bonmin{\textsc{BONMIN}\xspace}
\def\conopt{\textsc{CONOPT}\xspace}
\def\couenne{\textsc{Couenne}\xspace}
\def\cplex{\textsc{Cplex}\xspace}
\def\dicopt{\textsc{DICOPT}\xspace}
\def\xpress{\textsc{Xpress-Optimizer}\xspace}
\def\gurobi{\textsc{Gurobi}\xspace}
\def\ipopt{\textsc{Ipopt}\xspace}
\def\knitro{\textsc{Knitro}\xspace}
\def\lindo{\textsc{Lindo API}\xspace}
\def\lgo{\textsc{LGO}\xspace}
\def\minos{\textsc{MINOS}\xspace}
\def\mosek{\textsc{MOSEK}\xspace}
\def\msnlp{\textsc{MsNlp}\xspace}
\def\oqnlp{\textsc{OQNLP}\xspace}
\def\sbb{\textsc{SBB}\xspace}
\def\scip{\textsc{SCIP}\xspace}
\def\snopt{\textsc{SNOPT}\xspace}

@@

\newenvironment{proof}[1][Proof]{\textbf{#1.} }{\ \rule{0.5em}{0.5em}}

\def\remark{\stepcounter{theorem}\par\textbf{Remark}.
\ignorespaces}
\def\endremark{ \vbox{\hrule\hbox{%
    \vrule height1.3ex\hskip0.8ex\vrule}\hrule
   }\par}

\newenvironment{keywords}{\vspace{0.4in}\begin{quote}\small \em
\textbf{Keywords\/}:}{\end{quote}}
\fi

@@

%\listoftodos
\newpage

@@

\institute{Fabio Furini \at
           LAMSADE, Universit{\'e} Paris Dauphine, 75775 Paris, France.
           \email{fabio.furini@dauphine.fr}
%
\and
           Emiliano Traversi \at
           LIPN, Universit{\'e} de Paris 13, 93430 Villetaneuse, France.
           \email{emiliano.traversi@lipn.fr}
%
\and       Pietro Belotti \at
           Xpress-Optimizer team, FICO, Birmingham UK
           \email{pietrobelotti@fico.com}
%
\and       Antonio Frangioni \at
           Dipartimento di Informatica, Universit\`a di Pisa,
           Largo B. Pontecorvo 2, 56127 Pisa, Italy,
           \email{frangio@di.unipi.it}
%
\and       Ambros Gleixner \at
           Zuse Institute Berlin, Takustr. 7, 14195 Berlin, Germany.
           \email{gleixner@zib.de}
%
\and       Nick Gould \at
           STFC-Rutherford Appleton Laboratory, Chilton, Oxfordshire OX11 0QX,
           England.
           \email{nick.gould@stfc.ac.uk}
%
\and       Leo Liberti \at
           CNRS LIX, Ecole Polytechnique, 91128 Palaiseau, France.
           \email{liberti@lix.polytechnique.fr}
%
\and       Andrea Lodi \at
           Ecole Polytechnique de Montréal, Canada.               \email{andrea.lodi@polymtl.ca}
%
\and       Ruth Misener \at
           Department of Computing, Imperial College London, UK. \email{r.misener@imperial.ac.uk}
%
\and       Hans Mittelmann \at
           School of Mathematical and Statistical Sciences, Arizona State University,      Tempe, AZ 85287-1804, U.S.A.
\email{mittelmann@asu.edu}
%
\and       Nick Sahinidis \at
Chemical Engineering, Carnegie Mellon University, U.S.A. \email{sahinidis@cmu.edu}
%
\and       Stefan Vigerske \at
           GAMS Software GmbH, c/o Zuse Institute Berlin, Takustr. 7, 14195 Berlin, Germany.
           \email{svigerske@gams.com}
%
\and       Angelika Wiegele \at
Institut f{\"u}r Mathematik, Alpen-Adria-Universit{\"a}t Klagenfurt, 9020 Klagenfurt am W{\"o}rthersee, Austria.  \email{angelika.wiegele@aau.at}
           }

@@

\begin{abstract}
 This paper describes a new instance library for Quadratic Programming (QP), i.e., the family of continuous and (mixed)-integer optimization problems where either the objective function or the constrains (or both) are quadratic. 
 QP is a very ``varied'' class, comprising sub-classes of problems ranging from
 trivial to undecidable. Solution methods for QP are very diverse, ranging from
 entirely combinatorial ones to completely continuous ones, including many for
 which both aspects are fundamental. Selecting a set of instances of QP that is
 at the same time not overwhelmingly numerous and sufficiently challenging for the
 many different interested communities is therefore important. We propose a simple
 taxonomy for QP instances that leads to a systematic problem selection mechanism.
 We then briefly survey the field of QP, giving an overview of theory, methods and
 solvers. Finally we describe how the library was put together, and detail its final
 contents.
\end{abstract}

@@

\input{methods.tex}

@@

@@

%\input{QPLIB-4.tex}

@@

We are grateful to all the donors who provided instances for the library. We gratefully acknowledge the financial support of the Gaspard Monge Program for Optimization and operations research (PGMO)  and the logistic support of GAMS for having provided us the licence of their software. Finally, we would like to acknowledge the financial and networking support by the COST Action TD1207.
